Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-07 paper/main.tex
improved abstract

\begin{abstract}
  The goal of quantitative resource analysis is to provide developers
  with quantitative information about the runtime behavior of software
  at development time.  Recent years have seen tremendous progress in
  automatically deriving worst-case resource bounds.  Yet, many
  challenges in specifying, interactively deriving, formally
  certifying, and composing resource bounds remain unsolved.

  This paper describes a novel quantitative resource analysis
  framework that tackles these challenges for C programs.  The
  analysis framework consists of three parts.  First, the runtime
  resource consumption of programs is formalized with a parametric
  cost semantics for CompCert Clight.  Second, a quantitative Hoare
  logic that can be used for interactive bound development is
  implement and proved sound with respect to the cost semantics in the
  Coq Proof Assistant.  The logic is very expressive and shallow
  embedding enables a derived bound to be any function that is
  definable in Coq.  Third, an automatic amortized resource analysis
  for C programs that computes derivations in the quantitative Hoare
  logic is developed and implemented.  It is the first automatic
  amortized analysis that can derive bounds that depend on negative
  integers or differences between numbers, which is crucial to handle
  typical systems code.  Both, the quantitative logic and the
  automatic amortized analysis are naturally compositional and can be
  combined to semi-automatically derive global resource bounds.
  %
  An experimental evaluation demonstrates the practicability of the
  analysis framework.  The expressivity of the logic is shown by
  manually deriving customized bounds that are tailored to specific
  algorithms.  A comparison of the automatic amortized analysis with
  other automatic tools on 30 challenging examples from the literature
  and open-source software shows that the bounds derived by the
  automatic amortized analysis are often more precise.
\end{abstract}

>>>>

\begin{abstract}
  The goal of quantitative resource analysis is to provide developers
  with quantitative information about the runtime behavior of software
  at development time.  Recent years have seen tremendous progress in
  automatically deriving worst-case resource bounds, yet many
  challenges in specifying, interactively deriving, formally
  certifying, and composing resource bounds remain unsolved.

  This paper describes a novel quantitative resource analysis
  framework that tackles these challenges for C programs.  The
  analysis framework consists of three parts: First, a parametric cost
  semantics formalizes the resource consumption of CompCert Clight
  programs.  Second, a quantitative Hoare logic enables users to
  interactively develop resource bounds in the Coq Proof Assistant.
  The logic is proved sound with respect to the cost semantics, and
  shallow embedding enables a derived bound to be any function that is
  definable in Coq.  Third, an automatic amortized resource analysis
  for C programs computes derivations in the quantitative Hoare logic.
  It is the first automatic amortized analysis that can derive bounds
  that depend on negative integers or differences between numbers,
  which is crucial to handle typical systems code.  Both, the
  quantitative logic and the automatic amortized analysis are
  naturally compositional and can be combined to semi-automatically
  derive global resource bounds.
  %
  An experimental evaluation demonstrates the practicability of the
  analysis framework.  The expressivity of the logic is shown by
  manually deriving customized bounds that are tailored to specific
  algorithms.  A comparison of the automatic amortized analysis with
  other automatic tools on 30 challenging loop and recursion patterns
  from the literature and open-source software shows that the bounds
  derived by the automatic amortized analysis are often more precise.
\end{abstract}
